---
title: "RepData Peer Assessment #1"
author: "Nigel AR Henry"
date: "Sunday, May 17, 2015"
output: html_document
---


```{r}
activity<-read.csv("activity.csv")
```


```{r}
stepsPerDay <- tapply(activity$steps,activity$date,sum)
hist(stepsPerDay, main="Histogram of steps per day")
```


Mean steps per day is `r mean(stepsPerDay, na.rm=TRUE)`

Median steps per day is `r median(stepsPerDay, na.rm=TRUE)`

```{r}
tapply(activity$steps,activity$interval,mean,na.rm=T) -> avgStepsPerInterval
plot(unique(activity$interval), avgStepsPerInterval,
     type="l", main="Steps per 5 minute Interval, averaged across all days")
```

The 5-minute interval which has the most steps on average is `r which.max(avgStepsPerInterval)`

### Impute missing values
```{r}
imputedValues<-rep(avgStepsPerInterval, times=sum(is.na(stepsPerDay)));
activity$steps[is.na(activity$steps)] <- imputedValues

stepsPerDay <- tapply(activity$steps,activity$date,sum)
hist(stepsPerDay, main="Histogram of steps per day")
```


Mean steps per day is `r mean(stepsPerDay, na.rm=TRUE)`

Median steps per day is `r median(stepsPerDay, na.rm=TRUE)`

The mean value is unchanged, but the median value increases by 1.

### Weekdays and Weekends
```{r}
activity$weekday <- weekdays(as.Date(activity$date))
library(car)
activity$weekday <- recode(activity$weekday, "'Sunday'='Weekend';'Saturday'='Weekend'; else='Weekday'")
activity<-split(activity, activity$weekday)

par(mfrow=c(2,1))
plot(unique(activity$Weekday$interval), tapply(activity$Weekday$steps, activity$Weekday$interval, mean,na.rm=T),
     type="l", main="Steps per 5 minute Interval, averaged across Weekdays")
plot(unique(activity$Weekend$interval), tapply(activity$Weekend$steps, activity$Weekend$interval, mean,na.rm=T),
     type="l", main="Steps per 5 minute Interval, averaged across Weekdays")

```
